Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-03 paper/main.tex
comments paper y code con cego
split work on paper.

\section{Introduction}
% minimize the uncertainty in the final solutions or

@@

@@

Description of UMM and CEGO

@@

\newcommand{\minit}{\ensuremath{m_\text{ini}}}

@@

@@

@@

Bayesian optimization methods using a global GP model, such as CEGO, are know
to have trouble optimizing locally \citep{EriPeaGar2019scalable}. Our
intuition is that this problem becomes worse in rugged combinatorial
landscapes, where small steps may produce drastic changes.

>>>>

\section{Introduction}

Motivation: Manuel

In many practical optimization problems, the objective function contexts
% minimize the uncertainty in the final solutions or

Related work: Ekhine

Our contribution: Ekhine
\begin{itemize}
\item 
\end{itemize}

@@

MM, GMM, uMM; Ekhine

LOP: Ekhine

Quizás luego: PFSP y QAP

@@

CEGO: Manuel.

@@

\newcommand{\minit}{\ensuremath{m_\text{ini}}\xspace}

@@

Description of UMM: Ekhine

new approach: add sample, learn distri, sample distri

learn distri: uMM with param $\rho$ and binary search rho

sample: peakig distri

Quality guarantees

@@

Complete this with details of uMM: MANUEL

Computing system details: MANUEL

Describir como se generan las intancias de LOP: Ekhine

Describir las instancias: Ekhine

@@

Bayesian optimization methods using a global GP model, such as CEGO, are known
to have trouble optimizing locally \citep{EriPeaGar2019scalable}. Our
intuition is that this problem becomes worse in rugged combinatorial
landscapes, where small steps may produce drastic changes.
